Graphical Tests for Power Comparison of Competing Designs

### 2012-03-28 setup.tex
working on results

>>>>

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Error & $z$-value & $p$-value \\ 
  \hline
euclid & -0.08 & 0.39 & -0.21 & 0.84 \\ 
polar & -1.98 & 0.32 & -6.13 & 0.00 \\ [1pt]
  reflineTRUE & -0.14 & 0.26 & -0.53 & 0.59 \\ [1pt]
  sample\_size & 0.27 & 0.04 & 6.31 & 0.00 \\ [1pt]
  offset 90 & -0.43 & 0.37 & -1.18 & 0.24 \\ 
  offset 180 & -0.89 & 0.35 & -2.51 & 0.01 \\ 
  offset 270 & 0.21 & 0.38 & 0.55 & 0.58 \\ [1pt]
  polar:reflineTRUE & 0.51 & 0.35 & 1.44 & 0.15 \\ [1pt]
  polar:sample\_size & -0.23 & 0.05 & -5.02 & 0.00 \\ [1pt]
  polar:offset 90 & 0.64 & 0.49 & 1.30 & 0.20 \\ 
  polar:offset 180 & 0.91 & 0.47 & 1.92 & 0.05 \\ 
  polar:offset 270 & -0.73 & 0.54 & -1.35 & 0.18 \\
   \hline
\end{tabular}}
\end{center}
\caption{\label{tbl:correct} Model output for correct result. }
\end{table}

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & $z$ value & $p$ value from multcomp\\ 
  \hline
(Intercept) & 3.58 & 0.09 & 41.34 \\ 
  test\_parampolar & 0.22 & 0.10 & 2.17 \\ 
  reflineTRUE & 0.08 & 0.06 & 1.50 \\ 
  sample\_size & -0.03 & 0.00 & -8.73 \\ 
  offset90 & -0.06 & 0.08 & -0.72 \\ 
  offset180 & 0.16 & 0.08 & 2.07 \\ 
  offset270 & -0.04 & 0.07 & -0.54 \\ 
  test\_parampolar:reflineTRUE & -0.03 & 0.08 & -0.40 \\ 
  test\_parampolar:sample\_size & 0.03 & 0.01 & 6.25 \\ 
  test\_parampolar:offset90 & 0.14 & 0.11 & 1.23 \\ 
  test\_parampolar:offset180 & -0.17 & 0.11 & -1.55 \\ 
  test\_parampolar:offset270 & 0.17 & 0.11 & 1.50 \\ 
   \hline
\end{tabular}}
\end{center}
\caption{\label{tbl:time} Model output for (log) time taken. }
\end{table}

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
\rowcolors{2}{white}{lightgray}
\begin{tabular}{rrrr}
  \hline
 & Estimate & Std. Error & t value \\ 
  \hline
(Intercept) & 3.58 & 0.09 & 41.34 \\ 
  test\_parampolar & 0.22 & 0.10 & 2.17 \\ 
  reflineTRUE & 0.08 & 0.06 & 1.50 \\ 
  sample\_size & -0.03 & 0.00 & -8.73 \\ 
  offset90 & -0.06 & 0.08 & -0.72 \\ 
  offset180 & 0.16 & 0.08 & 2.07 \\ 
  offset270 & -0.04 & 0.07 & -0.54 \\ 
  test\_parampolar:reflineTRUE & -0.03 & 0.08 & -0.40 \\ 
  test\_parampolar:sample\_size & 0.03 & 0.01 & 6.25 \\ 
  test\_parampolar:offset90 & 0.14 & 0.11 & 1.23 \\ 
  test\_parampolar:offset180 & -0.17 & 0.11 & -1.55 \\ 
  test\_parampolar:offset270 & 0.17 & 0.11 & 1.50 \\ 
   \hline
\end{tabular}
}
\end{center}
\caption{\label{tbl:confidence} Model output for confidence level. }
\end{table}
